Parallel Global Optimization for Non-Convex Mixed-Integer Problems \thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2019-04-12 2019/RSD_Integer/RSD2019.tex
minor correction

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[misc,geometry]{ifsym}

@@

Identify the maximum current value of the index
\begin{equation}\label{Eq:19}
M=\max \left\{\nu = \nu(x_i), \ 1\leq i \leq k\right\}.
\end{equation}
\item
For all values of $\nu, \ 1\leq \nu \leq m+1$, calculate the values  
\begin{equation}\label{Eq:20}
\mu_\nu = \max \left\{ \frac{\left|z_i-z_j\right|}{\left(x_i-x_j\right)^{1/N}} : i,j \in I_\nu, 
j<i\right\}.
\end{equation}
If the set $I_\nu$ contains less than two elements or $\mu_\nu$ from (\ref{Eq:20}) equals zero, 
then assume $\mu_\nu=1$.
\item
For all non-empty sets $I_\nu$, $1 \leq \nu \leq m+1$, determine the values
\begin{equation}\label{Eq:21}
  z^\ast_\nu =  
   \begin{cases}
    -\epsilon_\nu,  \nu < M, \\
    \min{\left\{g_\nu(x_i):i\in I_\nu\right\}}, \nu = M,
   \end{cases}
\end{equation}
where $M$ is the maximum current value of the index, and the vector $\epsilon _R=\left(\epsilon_1,...,\epsilon_m\right)$ with positive coordinates is called the \textit{reserve vector} and is used as a parameter in the 
algorithm.
\item
For each interval $(x_{i-1},x_i)$,$1 \leq i \leq k+1$, calculate the \textit{characteristic} $R(i)$: 
\[
R(i)=\Delta_i+ \frac{(z_i-z_{i-1})^2}{(r_\nu\mu_\nu)^2\Delta_i}-2\frac{z_i+z_{i-1}-
2z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu=\nu(x_{i-1})=\nu(x_i),
\]
\[
R(i)= 2\Delta_i-4\frac{z_i-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu(x_{i-1})<\nu(x_i)=\nu,
\]
\[
R(i)= 2\Delta_i-4\frac{z_{i-1}-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu = \nu(x_{i-1})>\nu(x_i).
\]
where $\Delta_i=(x_i-x_{i-1})^{1/N}$, and the values $r_\nu>1, 1\leq\nu\leq m+1$, are used as 
parameters in the algorithm.
\item
Reorder the characteristics $R(i)$, $1\leq i \leq k+1$, from highest to lowest 	
\begin{equation}\label{Eq:23}
R(t_1)\geq R(t_2)\geq ... \geq R(t_{k})\geq R(t_{k+1})
\end{equation}
and choose $p$ largest characteristics with interval numbers $t_j, 1\leq j \leq p$.
\item
Carry out $p$ new trials in parallel at the points $x^{k+j}, 1 \leq j \leq p$, calculated by the 
formulae
\begin{eqnarray*}
& x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}, \; \nu(x_{t_j-1})\neq \nu(x_{t_j}), \\
& x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}- \frac{\mathrm{sign}(z_{t_j}-z_{t_j-
1})}{2r_\nu}\left[\frac{\left|z_{t_j}-z_{t_j-1}\right|}{\mu_\nu}\right]^N, \; \nu(x_{t_j-
1})=\nu(x_{t_j})=\nu. \\
\end{eqnarray*}

@@

GKLS~\cite{Gaviano} is a well known generator of the test problems for the continuous multiextremal 
optimization. It allows generating the functions of arbitrary dimensionality with 
known properties (the number of local minima, the size of their domains of attraction, the global 
minimizer, etc.).  
This generator of multiextremal functions is often used for the investigations of the global 
optimization algorithms ~\cite{Paulavicius2014,SergeyevKvasov2015,Lebedev2015,Gergel2015}. 
In Fig.~\ref{example} (a) and (b), the contour plots of two-dimensional GKLS functions are 
presented. Figures also shows the points of the trials performed by the method until the required 
accuracy $\epsilon=10^{-2}$ was achieved.

@@

>>>>

%\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[misc,geometry]{ifsym}

@@

Identify the maximum current value of the index
\begin{equation}\label{Eq:19}
M=\max \left\{\nu = \nu(x_i), \ 1\leq i \leq k\right\}.
\end{equation}
\item
For all values of $\nu, \ 1\leq \nu \leq m+1$, calculate the values  
\begin{equation}\label{Eq:20}
\mu_\nu = \max \left\{ \frac{\left|z_i-z_j\right|}{\left(x_i-x_j\right)^{1/N}} : i,j \in I_\nu, 
j<i\right\}.
\end{equation}
If the set $I_\nu$ contains less than two elements or $\mu_\nu$ from (\ref{Eq:20}) equals zero, 
then assume $\mu_\nu=1$.
\item
For all non-empty sets $I_\nu$, $1 \leq \nu \leq m+1$, determine the values
\begin{equation}\label{Eq:21}
  z^\ast_\nu =  
   \begin{cases}
    -\epsilon_\nu,  \nu < M, \\
    \min{\left\{g_\nu(x_i):i\in I_\nu\right\}}, \nu = M,
   \end{cases}
\end{equation}
where $M$ is the maximum current value of the index, and the vector $\epsilon _R=\left(\epsilon_1,...,\epsilon_m\right)$ with positive coordinates is called the \textit{reserve vector} and is used as a parameter in the 
algorithm.
\item
For each interval $(x_{i-1},x_i)$,$1 \leq i \leq k+1$, calculate the \textit{characteristic} $R(i)$: 
\[
R(i)=\Delta_i+ \frac{(z_i-z_{i-1})^2}{(r_\nu\mu_\nu)^2\Delta_i}-2\frac{z_i+z_{i-1}-
2z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu=\nu(x_{i-1})=\nu(x_i),
\]
\[
R(i)= 2\Delta_i-4\frac{z_i-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu(x_{i-1})<\nu(x_i)=\nu,
\]
\[
R(i)= 2\Delta_i-4\frac{z_{i-1}-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu = \nu(x_{i-1})>\nu(x_i).
\]
where $\Delta_i=(x_i-x_{i-1})^{1/N}$, and the values $r_\nu>1, 1\leq\nu\leq m+1$, are used as 
parameters in the algorithm.
\item
Reorder the characteristics $R(i)$, $1\leq i \leq k+1$, from highest to lowest 	
\begin{equation}\label{Eq:23}
R(t_1)\geq R(t_2)\geq ... \geq R(t_{k})\geq R(t_{k+1})
\end{equation}
and choose $p$ largest characteristics with interval numbers $t_j, 1\leq j \leq p$.
\item
Carry out $p$ new trials in parallel at the points $x^{k+j}, 1 \leq j \leq p$, calculated by the 
formulae
\begin{gather*}
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}, \; \nu(x_{t_j-1})\neq \nu(x_{t_j}),\\
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}- \frac{\mathrm{sign}(z_{t_j}-z_{t_j-
1})}{2r_\nu}\left[\frac{\left|z_{t_j}-z_{t_j-1}\right|}{\mu_\nu}\right]^N, \\
\nu(x_{t_j-1})=\nu(x_{t_j})=\nu.
\end{gather*}

@@

GKLS~\cite{Gaviano} is a well known generator of the test problems for the continuous multiextremal 
optimization. It allows generating the functions of arbitrary dimensionality with 
known properties (the number of local minima, the size of their domains of attraction, the global 
minimizer, etc.).  
This generator of multiextremal functions is often used for the investigations of the global 
optimization algorithms ~\cite{Paulavicius2014,SergeyevKvasov2015,Lebedev2015,Gergel2015,Barkalov2018}. 
In Fig.~\ref{example} (a) and (b), the contour plots of two-dimensional GKLS functions are 
presented. Figures also shows the points of the trials performed by the method until the required 
accuracy $\epsilon=10^{-2}$ was achieved.

@@

\bibitem{Barkalov2018}
Barkalov, K., Strongin, R.: Solving a set of global optimization problems by the parallel technique with uniform convergence. J. Glob. Optim. \textbf{71}(1), 21--36 (2018)
